Czech parliament meeting recordings as ASR training data

### 2020-04-25 2020-tsd-brno-svolocz/svolocz-anonymous.tex
svolocz: use samplepaper as template; add anonymized

%%%%%%%%%%%%%%%%%%%%%%% file typeinst.tex %%%%%%%%%%%%%%%%%%%%%%%%%
%
% This is the LaTeX source for the instructions to authors using
% the LaTeX document class 'llncs.cls' for contributions to
% the Lecture Notes in Computer Sciences series.
% http://www.springer.com/lncs       Springer Heidelberg 2006/05/04
%
% It may be used as a template for your own input - copy it
% to a new file with a new name and use it as the basis
% for your article.
%
% NB: the document class 'llncs' has its own and detailed documentation, see
% ftp://ftp.springer.de/data/pubftp/pub/tex/latex/llncs/latex2e/llncsdoc.pdf
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[runningheads,a4paper]{llncs}

\usepackage{amssymb}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{rotating}

\usepackage{url}
\urldef{\mailsa}\path|kruza@ufal.mff.cuni.cz|    
\newcommand{\keywords}[1]{\par\addvspace\baselineskip
\noindent\keywordname\enspace\ignorespaces#1}

\begin{document}

\mainmatter  % start of an individual contribution

% first the title is needed
\title{Czech parliament meeting recordings as ASR training data}

% a short form should be given in case it is too long for the running head
\titlerunning{Czech parliament meeting recordings as ASR training data}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Jan Oldřich Krůza}
%
\authorrunning{Jan Oldřich Krůza}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Institute of Formal and Applied Linguistics,\\
Faculty of Mathematics and Physics,\\
Charles University
\mailsa\\
\url{ufal.mff.cuni.cz}}

%
% NB: a more complex sample for affiliations and the mapping to the
% corresponding authors can be found in the file "llncs.dem"
% (search for the string "\mainmatter" where a contribution starts).
% "llncs.dem" accompanies the document class "llncs.cls".
%

\toctitle{Czech parliament meeting recordings as ASR training data}
\tocauthor{Jan Oldřich Krůza}
\maketitle

\begin{abstract}
I present a way to leverage the stenographed recordings of the Czech parliament
meetings for purposes of training a speech-to-text system. The article presents
a method for scraping the data, acquiring word-level alignment and selecting
reliable parts of the imprecise transcript. Finally, I present an ASR system
trained on these data.
\keywords{speech corpus, speech recognition, czech}
\end{abstract}

@@

\section*{Acknowledgments}

This work has been using language resources developed, stored and distributed by
the LINDAT/CLARIAH project of the Ministry of Education, Youth and Sports of the
Czech Republic (project LM2018101).

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.20 of 2017/10/04
%
\documentclass[runningheads]{llncs}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}

\begin{document}
%
\title{Czech parliament meeting recordings as ASR training data}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Anonymous Clerk\inst{1}\orcidID{0000-0000-0000-0000}}
%
\authorrunning{A. Clerk}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{The Ministry of Silly Walks,\\
Monty Python,\\
Hall of Fame\\
\email{monty-python@example.org}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
I present a way to leverage the stenographed recordings of the Czech parliament
meetings for purposes of training a speech-to-text system. The article presents
a method for scraping the data, acquiring word-level alignment and selecting
reliable parts of the imprecise transcript. Finally, I present an ASR system
trained on these data.
\keywords{speech corpus, speech recognition, czech}
\end{abstract}

@@
